---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# onsr

<!-- badges: start -->
[![R-CMD-check](https://github.com/kvasilopoulos/onsr/workflows/R-CMD-check/badge.svg)](https://github.com/kvasilopoulos/onsr/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/onsr)](https://CRAN.R-project.org/package=onsr)
<!-- badges: end -->

> **_NOTE:_** This API is currently in Beta and still being developed. Please be aware that as a result of this there may occasionally be breaking changes.


The goal of onsr is to to provide a client for the 'Office of National Statistics' ('ONS') API <https://api.beta.ons.gov.uk/v1>.  

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kvasilopoulos/onsr")
```
## Example

This is a basic example which shows you how to download data with `onsr`.

```{r example}
library(onsr)

ons_get(id = "ageing-population-estimates")

# All the available id names
ons_ids()
```

## Rate limiting

The ONS API applies rate limiting to ensure a high quality service is delivered to all users and to protect client applications from unexpected loops.

The following rate limits have been implemented:

* 120 requests per 10 seconds

* 200 requests per 1 minute

If you exceed these limits the API will return a 429 Too Many Requests HTTP status code and a Retry-After header containing the number of seconds until you may try your request again.
